\documentclass{resume} 

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Md Riazul Galib Niloy} % Your name

\address{+8801518337015 \\ niloygalib@gmail.com} 
\address{Dhaka, Bangladesh}


\begin{document}



\begin{rSection}{OBJECTIVE}

{Software Engineer with 2+ years of experience in web development, seeking a full-time role to apply and further develop my skills.}


\end{rSection}
%-----------------------------------------------
%	EDUCATION SECTION
%--------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Electrical Engineering}, Rajshahi University of Engineering and Technology \hfill {Expected 2025}\\
Relevant Coursework: C, JAVA, Object-Oriented Programming (OOP), Assembly Language.

{\bf Higher Secondary School Certificate}, GPA 5.00 out of 5.00, Dhaka Board \hfill {2017 - 2018}

{\bf Secondary School Certificate}, GPA 5.00 out of 5.00, Dhaka Board \hfill {2015 - 2017}



%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{@{}>{\bfseries}  l  @{\hspace{6ex}}l } 
Technical Skills & Node.js, Python Flask,Database Management (MongoDB, Firebase, Cloud Firestore)\\ 
Soft Skills & Problem-Solving, Adaptability, Team Collaboration, Communication\\ 
Additional Skills& API Integration (including Stripe), UI/UX Design, Project Management\\ 
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Software Engineer (Remote)} \hfill Jul 2023 - Present\\
Petapator \hfill \textit{Hong Kong, China }
 \begin{itemize}
    \itemsep -3pt {} 
     \item Developed secure APIs using Node.js and Python (Flask) frameworks.
     \item Crafted user-friendly UI and implemented secure login/authentication using Firebase.
    \item Integrated API responses seamlessly into the UI.
    \item Integrated Firebase authentication and Firebase datastore features.
    \item Integrated stripe with firebase functions.
 \end{itemize}

 \textbf{Backend Developer (Remote)} \hfill Jul 2022 - Jul 2023\\
Makebell \hfill \textit{Hong Kong, China }
 \begin{itemize}
    \itemsep -3pt {} 
     \item Developed secure APIs using Python (Flask) framework.
     \item Crafted user-friendly UI and implemented secure login/authentication using Firebase.
    \item Integrated stripe with firebase functions.
    \item Integrated Firebase authentication and Firebase datastore features.
 \end{itemize}
 
\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}

\item \textbf{Automation-House (Private)} 
    \newline {This project fetches all public top news from Bangladesh and shows them on a React UI.}
    \newline \textit{Technologies: JavaScript, React JS}
    
\item \textbf{Python-QR-Code-Generator (Public)} 
    \newline {A Python-based project for generating QR codes.}
    \newline \textit{Technologies: Python}
    
\item \textbf{Machine-Learning (Public)} 
    \newline {A collection of machine learning projects using Jupyter Notebook.}
    \newline \textit{Technologies: Jupyter Notebook}
    
\item \textbf{Firebase-Using-Flask (Public)} 
    \newline {A Python project demonstrating the use of Firebase with Flask.}
    \newline \textit{Technologies: Python}

\item \textbf{Bangla-Number-Plate-Extraction (Public)} 
    \newline {This repository contains the code and resources for training and deploying a YOLOv8-based model for Bangla Number Plate Extraction. With a dataset of 2000 annotated images for training and validation.}
    \newline \textit{Technologies: Python,OpenCV,Raspberry Pi}
    \newline \textit{License: MIT}

\item \textbf{Intelligent-Car-Parking-System (Public)} 
    \newline {A project focused on developing an intelligent parking system.}

\item \textbf{BD-License-Plate-Detection-and-Text-Recognition (Private)} 
    \newline {This repository houses a comprehensive solution for license plate detection and text recognition in Bangladesh using state-of-the-art deep learning technology.}
    \newline \textit{Technologies: Python} \newline \textit{License: MIT}
    
\item \textbf{Python-TicTacToe-GUI (Public)} 
    \newline {A Python-based Tic Tac Toe game designed with HTML and CSS, running on a Python platform.}
    \newline \textit{Technologies: Python, HTML, CSS}
    
\item \textbf{Arduino-Based Wireless Robot} 
    \newline {An Arduino-based line follower robot project.}
    \newline \textit{Technologies: Arduino IDE}

\end{rSection}


%----------------------------------------------------------------------------------------
\begin{rSection}{EXTRA-CURRICULAR ACTIVITIES}

\item \textbf{Academic Tutor for 11th and 12th Grade Students} \\
Provided tutoring in subjects such as Mathematics and Physics, helping students prepare for their exams and improve their academic performance. This role involved creating customized study plans, explaining complex concepts, and fostering a positive learning environment.

\end{rSection}




\end{document}
